Using an SMT engine to generate Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-20 2017-Xudong-SMT/ActaInformatica.tex
Improve Alg 1, add more explanation for Alg 1,2
In Alg 1, add two functions at the end of the algorithm, the explanation part is just below the Alg 1.
Add more explanation in 4.1, as Alg 2 is just for pNets, there is no more things to add.

\begin{algorithm}[h]
  \caption{Open Automaton Generation}
  \label{alg1}
\begin{algorithmic}[1]
\Require A pNet $P$ (can be a pLTS, but not a hole)
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
\While{!$\mathit{isEmpty}(U)$}
	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
	\For {each $\mathit{OT} \in \mathit{OTs}$}
          \State Add $\mathit{OT}$ to $L$;
          \State Let $S'$ be the target state of $\mathit{OT}$
          Add $S'$ to the unexplored states if necessary:
	  \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
	  \EndFor
\EndWhile
\State \TODO{Xudong:Prune the unsatisfiable open transitions in $L$ using the SMT
  solver;
   and add a call to ``compute the reachable sub-automaton'';}
\State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;

@@

@@

In a pLTS, there may be several incoming transitions 
that assign potentially different (symbolic) values to a state variable.
To handle such cases, the algorithm manages, for each pLTS state, a
list of expressions collected from the assignments of each state
variable. %% $v$.
%% The list we used contains triples <$v$, $S$, $AssignRH$> 
%% where $v$ is the variable in pLTS, $S$ is its owner state and
%% $AssignRH$ is a list of expressions over other variables in the right
%% hand side of assignments of $v$.
% As a pragmatic extension to the formal definition, we also manage
% ``global variables'', defined in all states of the pLTS.
For a global state in the open automaton, the set of state
variables (which may be used in an outgoing transition) %% will simply be
is the disjoint union
of sets of state variables of the individual pLTS states constituting this
global state.
\TODO{Xudong: speciy more precisely what is done, and at which point
  in the MakeTransitions algo}
%There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables). There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results. In order to avoid such mistakes, 
\TODO{Eric: these sets of assignment collect potential assignments from all OTs
  in the generated automaton. If we prune the generated state
  space, we will get less assignements, and potentialy also get better
  minimization... May be move this to ``smart'' section}

>>>>

\begin{algorithm}[h]
  \caption{Open Automaton Generation}
  \label{alg1}
\begin{algorithmic}[1]
\Require A pNet $P$ (can be a pLTS, but not a hole)
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
\While{!$\mathit{isEmpty}(U)$}
	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
	\For {each $\mathit{OT} \in \mathit{OTs}$}
          \State Add $\mathit{OT}$ to $L$;
          \State Let $S'$ be the target state of $\mathit{OT}$
          Add $S'$ to the unexplored states if necessary:
	  \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
	  \EndFor
\EndWhile
\State \QIN{\texttt{filterUnsatTransition}(L)}
\State \QIN{\texttt{filterNoPrecursor}(L)}
\State \TODO{Xudong:Prune the unsatisfiable open transitions in $L$ using the SMT
  solver;
   and add a call to ``compute the reachable sub-automaton'';}
\State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;

@@

\QIN{The function \texttt{filterUnsatTransition}() realizes exactly what described above, completing the open transitions pruning work.}

\QIN{The function \texttt{filterNoPrecursor}() detects the unreachable states which has no precursor states in the pruned automaton and removes them.}

@@

In a pLTS, there may be several incoming transitions 
that assign potentially different (symbolic) values to a state variable.
To handle such cases, the algorithm manages a
list of assignment expressions for each pLTS state. 
\QIN{Every time the MakeTransitions
algorithm is applied on a pLTS, it collects the expressions from the $Post$ in each transition.
As there is no assignments collecting work on a pNet node, it is not shown in Algorithm~\ref{alg2}.}
%% $v$.
%% The list we used contains triples <$v$, $S$, $AssignRH$> 
%% where $v$ is the variable in pLTS, $S$ is its owner state and
%% $AssignRH$ is a list of expressions over other variables in the right
%% hand side of assignments of $v$.
% As a pragmatic extension to the formal definition, we also manage
% ``global variables'', defined in all states of the pLTS.

For a global state in the open automaton, the set of state
variables (which may be used in an outgoing transition) %% will simply be
is the disjoint union
of sets of state variables of the individual pLTS states constituting this
global state.
\TODO{Xudong: speciy more precisely what is done, and at which point
  in the MakeTransitions algo}
%There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables). There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results. In order to avoid such mistakes, 
\TODO{Eric: these sets of assignment collect potential assignments from all OTs
  in the generated automaton. If we prune the generated state
  space, we will get less assignements, and potentialy also get better
  minimization... May be move this to ``smart'' section}
